Kids SUMs Summary

### 2020-01-16 dustrak_data_cleaning.Rmd
commit from new computer

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 10 Jan 2020"
output: pdf_document
---

@@

>>>>

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Save cleaned dataset
```{r}
kids_pm_new <- read_rds("Output/kids_pm_new.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

pm_clean <- kids_pm_new %>% 
  mutate(home_winter_id = as.character(home_winter_id)) %>% 
  select(-home, -treatment) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(pm_clean, "Output/pm_clean.rds")
```

### 2020-01-16 home_char_act_summary.Rmd
commit from new computer

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

>>>>

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 15 Jan 2020"
output:
  word_document: default
  pdf_document: default
---

### 2020-01-16 home_child_data_cleaning.Rmd
SUMs cleaning
commit from new computer

#write_rds(kids_demographics, "Output/kids_combined_demographics.rds")

@@

>>>>

# write_rds(kids_demographics, "Output/kids_combined_demographics.rds")

@@

# Clean demographics data
```{r}
kids_demographics <- read_rds("Output/kids_combined_demographics.rds")

demographics_clean <- kids_demographics %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash)

# write_rds(demographics_clean, "Output/demographics_clean.rds")
```

### 2020-01-16 indoor_temp_rh_cleaning.Rmd
commit from new computer

---
title: "KidsAIR indoor temp and humidity cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Summarize temp/rh data
```{r}
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")

temp_rh_summary <- indoor_temp_rh_clean %>%
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  t()
temp_rh_summary
```

>>>>

---
title: "KidsAIR indoor temp and humidity cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

### 2020-01-16 stove_grade_usage_cleaning.Rmd
commit from new computer

---
title: "KidsAIR wood stove grades and usage"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Summary data for stove grades
```{r}
# Load dataset
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")

stove_grade_summary <- stove_grades_clean %>% 
  group_by(area, stove_grade) %>% 
  summarize(n())
stove_grade_summary
```

@@

stove_use_clean <- kids_stove_use %>% 
  replace_with_na(replace = list(wood_cords = -999, wood_cords = 0)) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

@@

# Summary data for stove use
```{r}
# Load dataset
stove_use_clean <- read_rds("Output/stove_use_clean.rds")

# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  group_by(area) %>% 
  summarize(mean(wood_cords, na.rm = TRUE), 
            min(wood_cords, na.rm = TRUE), 
            median(wood_cords, na.rm = TRUE), 
            max(wood_cords, na.rm = TRUE))
stove_use_summary

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- stove_use_clean %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -wood_cords) 
lapply(table_list, table)

## Select specific var to assess individually/group by area
table(stove_use_clean$burn_level, stove_use_clean$area, useNA = "ifany")
```

>>>>

---
title: "KidsAIR wood stove grades and usage"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

@@

stove_use_clean <- kids_stove_use %>% 
  replace_with_na(replace = list(wood_cords = -999, wood_cords = 0)) %>% 
  mutate(wood_collect = factor(wood_collect,
                               levels = c("Less than 1 week",
                                          "Between 1 week and 1 month",
                                          "Between 1 month and 3 months",
                                          "Between 3 months and 6 months",
                                          "Between 6 months and 1 year",
                                          "More than 1 year"),
                               labels = c("< 1 week",
                                          "1 week to 1 mo",
                                          "1 mo to 3 mo",
                                          "3 mo to 6 mo",
                                          "6 mo to 1 year",
                                          "> 1 yr"))) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

@@

### 2020-01-16 sums_summary.Rmd
commit from new computer

---
title: "Kids SUMs Summary"
author: "Ethan Walker"
date: "Started 9 Jan 2020, Updated 9 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

@@

# Summary stats
```{r}
sums_summary <- sums_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean Temp" = mean(temp_c_sums, na.rm = TRUE), 
            "SD Temp" = sd(temp_c_sums, na.rm = TRUE),
            "Min Temp" = min(temp_c_sums, na.rm = TRUE), 
            "Median Temp" = median(temp_c_sums, na.rm = TRUE),
            "Max Temp" = max(temp_c_sums, na.rm = TRUE))
```

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_sums <- sums_clean %>%
  ggplot(aes(area, temp_c_sums)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(-50, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Temperature (degrees C)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_sums
```

>>>>

---
title: "Kids SUMs Summary"
author: "Ethan Walker"
date: "Started 9 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE)
```

@@

# Summary stats by area (winter)
```{r}
sums_summary <- sums_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area, winter_id) %>% 
  summarize("n" = n(),
            "Mean Temp" = mean(temp_c_sums, na.rm = TRUE), 
            "SD Temp" = sd(temp_c_sums, na.rm = TRUE),
            "Min Temp" = min(temp_c_sums, na.rm = TRUE), 
            "Median Temp" = median(temp_c_sums, na.rm = TRUE),
            "Max Temp" = max(temp_c_sums, na.rm = TRUE)) %>% 
  select(-area, -winter_id) %>% 
  t()

kable(sums_summary, col.names = c("Alaska (1)", "Alaska (2)",
                                  "Navajo (1)", "Navajo (2)",
                                  "Montana (1)", "Montana (2)"), 
      digits = 1, align = "c")
```

# Boxplots for SUMs temp (C) by study area - Winter 1
```{r, fig.height=6, fig.width=5}
boxplots_kids_sums <- sums_clean %>%
  filter(winter_id == 1) %>% 
  ggplot(aes(area, temp_c_sums)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(-50, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Temperature (degrees C)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_sums
```

# Boxplots for SUMs temp (C) by study area - Winter 2
```{r, fig.height=6, fig.width=5}
boxplots_kids_sums <- sums_clean %>%
  filter(winter_id == 2) %>% 
  ggplot(aes(area, temp_c_sums)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(-50, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Temperature (degrees C)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_sums
```
